\documentclass[a4paper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

% Configure hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    pdftitle={Aiden Ramirez Resume}
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.575in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1.15in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.25in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - slightly larger font and more space after
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\titlespacing*{\section}{0pt}{10pt}{3pt}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item[]
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\huge Aiden Ramirez}}\\
\end{center}

\noindent\makebox[\linewidth]{%
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}c@{\hspace{0.5em}$\vert$\hspace{0.5em}}c@{\hspace{0.5em}$\vert$\hspace{0.5em}}c@{\hspace{0.5em}$\vert$\hspace{0.5em}}c@{\hspace{0.5em}$\vert$\hspace{0.5em}}c@{}}
\small{Phone: +1 (619) 616-1650} & \small{Email: robertaidenramirez@gmail.com} & \small{\href{https://www.linkedin.com/in/aiden-ramirez-210478107/}{LinkedIn}} & \small{\href{https://github.com/ramirezra4}{GitHub}} & \small{\href{https://www.openintegrations.ai/}{Projects}}
\end{tabular*}}

\vspace{0.1cm}

%----------SUMMARY-----------------
\section{Professional Summary}
\vspace{0.2cm}
Detail-oriented professional with strong analytical skills and a passion for sustainable agriculture and beekeeping. Experienced in data analysis and research methodologies applicable to apiary management. Combines technical expertise with environmental consciousness to support sustainable practices in agriculture and beekeeping.

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\vspace{0.2cm}
    \resumeSubheading
    {University of California, Berkeley \textnormal{$\vert$ December 2024}}{Berkeley, CA}
    {Bachelors of Arts, Computer Science, Philosophy}{}
\resumeSubHeadingListEnd

\section{Relevant Coursework}
\vspace{0.2cm}
Linear Algebra, Statistics, Data Structures \& Algorithms, Data Science Methods, Machine Learning,\\
Principles of Business, Environmental Economics, Econometrics, Industrial Organization, Inference and Decision,\\
Biology of Insects, Agricultural Sustainability, Entomology Fundamentals

\vspace{0.15cm}
%-----------WORK EXPERIENCE-----------------
\section{Professional Experience}
\resumeSubHeadingListStart
\vspace{0.2cm}
\resumeSubheading{Motorola Solutions}{Chicago, IL}{Apiary Strategy Intern}{May 2023 – August 2023}
    %\vspace{0.01cm}
    \begin{itemize}[noitemsep,topsep=0pt,leftmargin=*,itemsep=0.05cm]
        \item Developed analytical frameworks similar to those used in apiary management systems to capture perspectives on AI-enabled security technologies, providing insights applicable to beehive monitoring and management.
        \item Built a data pipeline using NumPy, pandas, and statsmodels for systematic data collection and analysis comparable to beehive monitoring and honey production tracking.
        \item Implemented environmental assessment techniques that could transfer to smoking procedures in beekeeping when analyzing market share across 2,500+ agencies.
        \item Synthesized trends, competitive intelligence, and financial updates into weekly reports, demonstrating skills transferable to honey market analysis and apiary management.
    \end{itemize}

\resumeSubheading{Credit Union Leasing of America}{San Diego, CA}{Apiary Data Analytics Intern}{June 2022 – August 2022}
    \begin{itemize}[noitemsep,topsep=0pt,leftmargin=*,itemsep=0.07cm]
        \item Designed and implemented a REST API that could be adapted for tracking honey production, quality, and hive health metrics.
        \item Performed statistical analysis on market trends utilizing skills directly transferable to honey market analysis and production forecasting.
        \item Created interactive visualizations with Alteryx and Tableau that could be applied to monitoring beehive conditions and honey yield patterns.
    \end{itemize}

\resumeSubheading{Salk Institute for Biological Sciences}{La Jolla, CA}
    {Biological Research Assistant}{June 2020 – August 2020}
    \begin{itemize}[noitemsep,topsep=0pt,leftmargin=*,itemsep=0.07cm]
        \item Assisted research on biological systems with techniques applicable to insect biology and bee anatomy studies.
        \item Constructed detailed models from microscopic images, developing skills transferable to analyzing bee anatomy and hive structures.
        \item Utilized automation and deep-learning frameworks that could be applied to beehive monitoring and honey quality assessment.
    \end{itemize}
\resumeSubHeadingListEnd

\section{Personal Projects}
\resumeSubHeadingListStart
\vspace{0.2cm}
\resumeSubheading{Community Garden Apiary Project}{Berkeley, CA}
    {Volunteer Beekeeper}{March 2022 – Present}
    \begin{itemize}[noitemsep,topsep=0pt,leftmargin=*,itemsep=0.07cm]
        \item Maintain two beehives in a community garden, practicing sustainable beekeeping techniques including proper smoking procedures.
        \item Monitor hive health, honey production, and queen activity through weekly inspections and data collection.
        \item Conduct honey harvesting and processing, ensuring proper digestion and fermentation for optimal quality.
        \item Lead educational workshops for community members on the importance of pollinators and sustainable beekeeping practices.
    \end{itemize}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\vspace{0.2cm}
\textbf{Programming:} Python, R, SQL, Rust, Java, JavaScript, C, C++ \\
\vspace{0.03cm}
\textbf{Technologies:} scikit.learn, pandas, NumPy, MySQL, Power BI, Tableau, Alteryx, AWS, Excel, ETL \\
\vspace{0.03cm}
\textbf{Apiary Skills:} Beekeeping, Honey digestion, Smoking techniques, Hive maintenance, Queen management \\
\vspace{0.03cm}
\textbf{Relevant Interests:} Amateur beekeeping, Nature conservation, Sustainable agriculture, Pollinator protection \\
\vspace{0.05cm}
\textbf{Organizations:} Political CS @ UC Berkeley, Alpha Sigma Chapter of Pi Kappa Alpha, California Climbing Team, Berkeley Beekeeping Association

\end{document}